%==============================================================================
%  Shahriar Ahmed Seam — CV
%  Compile:  latexmk -pdf cv.tex     (or: pdflatex cv.tex)
%==============================================================================
\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% Computer Modern (lmodern) — same typeface as Abrar's CV
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[left=0.65in,right=0.65in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

% PDF metadata
\hypersetup{
  pdftitle={Shahriar Ahmed Seam - CV},
  pdfauthor={Shahriar Ahmed Seam},
  pdfsubject={AI/ML Engineer},
  pdfkeywords={Machine Learning, LLM, RAG, Agentic AI, MLOps, Full Stack, Python, C++}
}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Section headings: Small Caps + hrule (Abrar's style)
\titleformat{\section}{\large\scshape}{}{0em}{}[\vspace{1pt}\hrule\vspace{1pt}]
\titlespacing*{\section}{0pt}{3pt}{2pt}

% Compact bullet list
\newlist{tight}{itemize}{1}
\setlist[tight]{leftmargin=1.4em,label=\textbullet,itemsep=0pt,topsep=1pt,parsep=0pt}

\begin{document}

%------------------------------------------------------------------ HEADER
\begin{center}
    {\Large \textbf{Shahriar Ahmed Seam}}\\[4pt]
    \small
    \href{mailto:shahriarseam17@gmail.com}{shahriarseam17@gmail.com} \ | \
    \href{https://www.linkedin.com/in/shahriar-ahmed-seam/}{LinkedIn} \ | \
    \href{https://github.com/shahriar-ahmed-seam}{Github} \ | \
    {+880 1700-942829}
\end{center}

%------------------------------------------------------------------ SUMMARY
\section{Summary}
I am a Computer Science and Engineering student at BUET and an AI/ML engineer working across the
modern AI stack, from LLMs, RAG, and agentic systems to generative AI, NLP, computer vision, and
diffusion models. Alongside this, I research and fine-tune LLMs and turn them into production-grade
systems built on fault-tolerant microservices and solid backend, full-stack, and DevOps engineering.
To me, AI should be a core, observable part of production infrastructure, not just an add-on.

%------------------------------------------------------------------ EDUCATION
\section{Education}

\textbf{Bangladesh University of Engineering and Technology (BUET)}\hfill\textit{Expected December 2027}\\[1pt]
Bachelor of Science in Computer Science \& Engineering\par\vspace{3pt}

\textbf{Notre Dame College}\hfill\textit{June 2020}\\[1pt]
Higher Secondary Certificate, Science\par\vspace{1pt}

%------------------------------------------------------------------ EXPERIENCE
\section{Experience}

\textbf{Somokolon Labs}\hfill \textit{January 2026 -- Present}\\[1pt]
\textit{Founder \& AI/ML Engineer}\hfill\href{https://somokolonlabs.com}{somokolonlabs.com}
\begin{tight}
    \item Founded and run an AI and software studio that ships LLM, RAG, generative-AI, and full-stack products end to end.
    \item Delivered production point-of-sale (POS) software for small retail businesses, from requirements gathering through deployment.
    \item Own the full lifecycle: research, engineering, CI/CD, cloud deployment, and monitoring across the studio's shared infrastructure.
\end{tight}\vspace{2pt}

%------------------------------------------------------------------ PROJECTS
\section{Projects}

\begin{tight}
    \item \textbf{Nexus Agent Orchestrator} (\textbf{LangGraph} + \textbf{FastAPI} + \textbf{Next.js} + \textbf{pgvector}): Multi-agent platform (plan $\rightarrow$ research $\rightarrow$ code $\rightarrow$ critique) with RAG over documents; runs fully offline with local models.
    \item \textbf{Vector Vault DB} (\textbf{C++17} + \textbf{AVX-512} + \textbf{pybind11}): Vector database built from scratch with HNSW/IVF indexes and AVX-512 distance kernels; Python bindings for search over millions of vectors.
    \item \textbf{ResoNet} (\textbf{ONNX} + \textbf{ResNet} + \textbf{Dart} + \textbf{Edge AI}): On-device respiratory screening from cough audio; reimplemented preprocessing and ResNet18 in pure Dart, cutting the app from 600\,MB+ to $\sim$70\,MB with no accuracy loss.
    \item \textbf{HillTrack Pulse} (\textbf{DBSCAN} + \textbf{FastAPI} + \textbf{Ollama} + \textbf{Gemini}): Offline-first outbreak-detection and medical-consultation system for low-connectivity rural regions of Bangladesh.
\end{tight}\vspace{2pt}

%------------------------------------------------------------------ SKILLS
\section{Programming Skills}

\begin{tight}
    \item \textbf{Languages}: Python, C++, TypeScript/JavaScript, Go, Java, SQL
    \item \textbf{AI/ML}: PyTorch, LLMs \& RAG, Agentic AI (LangGraph, LangChain), Generative AI, NLP, Computer Vision, Diffusion Models, Hugging Face, ONNX
    \item \textbf{Backend \& Full Stack}: FastAPI, Node.js/Express, Spring Boot, React, Next.js, PostgreSQL, Redis
    \item \textbf{DevOps \& MLOps}: Docker, Kubernetes, Kafka, CI/CD (GitHub Actions), AWS, Ollama, Git
\end{tight}\vspace{2pt}

%------------------------------------------------------------------ LEADERSHIP
\section{Leadership \& Organizational Experience}

\textbf{Secretary} (LWS), Notre Dame Science Club\hfill\textit{May 2020 -- May 2021}\par
\textbf{Member}, BUET Robotics Club\par
\textbf{Volunteer}, Quantum Foundation Blood Donation Program\vspace{2pt}

%------------------------------------------------------------------ AWARDS
\section{Awards \& Achievements}

\begin{tight}
    \item \textbf{Top 5 Finalist}, Future Builders 2025 (AI-Driven Cognitive Innovation Hackathon) --- built \textit{HillTrack Pulse}, an offline-first healthcare platform for rural Bangladesh.
    \item \textbf{Finalist (Top 28 Teams, MarTech \& Branding)}, INFINITE AI Builders --- built \textit{AIgnis}, an AI-driven autonomous marketing-campaign system.
    \item \textbf{Finalist}, BUET CSE Fest Hackathon --- built \textit{OrionStream ML}, an event-driven ML inference platform.
    \item \textbf{Regional Champion}, Bangladesh Physics Olympiad; National Participant, Physics \& Astronomy Olympiads
\end{tight}

\end{document}
